Update Meeting: 03-11-2021

### 2021-11-03 analysis/update_meeting_03_11_2021.Rmd
wflow_publish("analysis/update_meeting_03_11_2021.Rmd")

household_MR_summary_sub <- household_MR_summary %>% dplyr::select(exposure_ID, outcome_ID, IVW_meta_beta, IVW_meta_pval) %>% unique()
MVMR_uniMR_comparison.DT <- inner_join(household_MR_summary_sub, household_MVMR_BF.DT)  %>% dplyr::select(exposure_ID, outcome_ID, exposure_description, outcome_description, corr_traits, everything())
format_round_cols <- colnames(dplyr::select_if(MVMR_uniMR_comparison.DT, is.numeric))

@@

>>>>

household_MR_summary_sub <- household_MR_summary %>% dplyr::select(exposure_ID, outcome_ID, IVW_meta_beta, IVW_meta_se, IVW_meta_pval) %>% unique()
MVMR_uniMR_comparison.DT <- inner_join(household_MR_summary_sub, household_MVMR_BF.DT)  %>% dplyr::select(exposure_ID, outcome_ID, exposure_description, outcome_description, corr_traits, everything())
format_round_cols <- colnames(dplyr::select_if(MVMR_uniMR_comparison.DT, is.numeric))

@@

```{r direct_vs_indirect_effects_plot, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE), message=FALSE}

plot_data <-  inner_join(household_MR_summary_sub, household_MVMR_summary.DT)  %>% dplyr::select(exposure_ID, outcome_ID, exposure_description, outcome_description, corr_traits, IVW_meta_beta, IVW_meta_se, yi_meta_beta, yi_meta_se, xi_meta_beta, xi_meta_se, xp_meta_beta, xp_meta_se) %>% unique()

#bquote('x axis'~(Å^2))
#expression(Sepal~Length[cm])

#Indirect~effect~of~X[i]~on~Y[p]~(from~univariate~MR)
#xlab <- bquote('Indirect effect of x_i on y_p (from univariate MR)'~(Å^2))

plot <-
  ggplot2::ggplot(data = plot_data, ggplot2::aes(x = IVW_meta_beta,
                                                 y = xi_meta_beta)) +
  geom_point(alpha = 3 / 4) +
  geom_smooth(
    mapping = aes(x = IVW_meta_beta, y = xi_meta_beta),
    method = "lm",
    se = FALSE,
    formula = y ~ x + 0,
    fullrange = TRUE,
    color = custom_col[4]
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(ymin = xi_meta_beta - xi_meta_se, ymax = xi_meta_beta + xi_meta_se),
    colour = "grey",
    width = 0
  ) +
  ggplot2::geom_errorbarh(
    ggplot2::aes(xmin = IVW_meta_beta - IVW_meta_se, xmax = IVW_meta_beta + IVW_meta_se),
    colour = "grey",
    height = 0
  ) +
  theme_minimal() +
  ggplot2::labs(
    x = expression(Indirect~effect~of~X[i]~on~Y[p]~(from~univariate~MR)),
    y = expression(Direct~effect~of~X[i]~on~Y[p]~(from~MVMR))
  ) + 
  geom_abline(slope=1, intercept=0)

plot
